MCC Preference Kids

### 2018-11-23 stats/kids_Ex3_pref.Rmd
start working on kids model predictions

d_raw <-raw_data

d_raw

@@

```{r plot by age, echo= FALSE}
pf1 <- d %>%
      filter(trial == "filler1" | trial == "filler2")%>%
  group_by(control,subage, subid) %>%
  summarise(correct = mean(correct))

@@

ggplot() +
  geom_jitter(data = pf1, aes(x = control, y = correct, col = control, alpha = .2),width = .3,height = .025)+
  geom_pointrange(data = pf2, aes(x = control, y = mean, col = control, ymin = ci_lower, ymax = ci_upper),size = .8)+
  geom_hline(yintercept = 0.5, lty=2)+
  labs(x="",y="Proportion Expected Choice")+
  theme_few() +
  facet_wrap(~subage)+
  ylim(-0.05,1.05)+
  guides(alpha = F)+ 
  theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())+
  scale_colour_solarized(name="Control",
                     breaks=c("false", "true"),
                     labels=c("No", "Yes"))
```

@@

p1 <- d %>%
  filter(trial != "filler1",
         trial != "filler2")%>%
  group_by(control,subage, subid) %>%
  summarise(correct = mean(correct))

@@

ggplot() +
  geom_jitter(data = p1, aes(x = control, y = correct, col = control, alpha = .2),width = .3,height = .025)+
  geom_pointrange(data = p2, aes(x = control, y = mean, col = control, ymin = ci_lower, ymax = ci_upper),size = .8)+
  geom_hline(yintercept = 0.5, lty=2)+
  labs(x="",y="Proportion Expected Choice")+
  theme_few() +
  facet_wrap(~subage)+
  ylim(-0.05,1.05)+
  guides(alpha = F)+ 
  theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())+
  scale_colour_solarized(name="Control",
                     breaks=c("false", "true"),
                     labels=c("No", "Yes"))
```

# Plot overall test

```{r plot across age, echo = F }
p3 <- d %>%
  filter(trial != "filler1",
  trial != "filler2")%>%
  group_by(control, subid) %>%
  summarise(correct = mean(correct))

p4 <- p3 %>%
  multi_boot_standard(col = "correct")

ggplot() +
  geom_jitter(data = p3, aes(x = control, y = correct, col = control, alpha = .2),width = .3,height = .025)+
  geom_pointrange(data = p4, aes(x = control, y = mean, col = control, ymin = ci_lower, ymax = ci_upper),size = .8)+
  geom_hline(yintercept = 0.5, lty=2)+
  labs(x="",y="Proportion Expected Choice")+
  theme_few() +
  ylim(-0.05,1.05)+
  guides(alpha = F)+ 
  theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())+
  scale_colour_solarized(name="Control",
                     breaks=c("false", "true"),
                     labels=c("No", "Yes"))

>>>>

d <-raw_data

@@

```{r plot by age, echo= FALSE}
pf1 <- d %>%
      filter(trial == "filler1" | trial == "filler2")%>%
  group_by(subage, subid) %>%
  summarise(correct = mean(correct_inf))

@@

ggplot() +
  geom_jitter(data = pf1, aes(x = subage, y = correct, col = subage, alpha = .2),width = .1,height = .025)+
  geom_pointrange(data = pf2, aes(x = subage, y = mean, col = subage, ymin = ci_lower, ymax = ci_upper),size = .8)+
  geom_hline(yintercept = 0.5, lty=2)+
  labs(x="",y="Proportion Expected Choice")+
  theme_few() +
  ylim(-0.05,1.05)+
  guides(alpha = F)+ 
  theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())
```

@@

p1 <- d %>%
  filter(trial != "filler1",
         trial != "filler2")%>%
  group_by(speaker, alignment ,subage, subid) %>%
  summarise(correct = mean(correct_inf))

@@

ggplot() +
  geom_jitter(data = p1, aes(x = alignment, y = correct, col = alignment, alpha = .2),width = .3,height = .025)+
  geom_pointrange(data = p2, aes(x = alignment, y = mean, col = alignment, ymin = ci_lower, ymax = ci_upper),size = .8)+
  geom_hline(yintercept = 0.5, lty=2)+
  labs(x="",y="Proportion Expected Choice")+
  theme_few() +
  facet_grid(subage~speaker)+
  ylim(-0.05,1.05)+
  guides(alpha = F)+ 
  scale_colour_solarized(name="Control",
                     breaks=c("false", "true"),
                     labels=c("No", "Yes"))
```

### 2018-11-23 stats/kids_model_predictions.Rmd
start working on kids model predictions

---
title: "MCC Model Predictions"
author: "Manuel Bohn"
date: "15 6 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

load("model.predictions.RData")

library(tidyverse)
library(knitr)
library(ggthemes)
library(langcog)
library(rwebppl)
library(coda)

@@

@@

```{r rsaUtils, include = FALSE}
rsaUtils <- '
var all_objects = [
{ shape: "triangle", id:1, location: 1},  
{ shape: "triangle", id:2, location: 2},
{ shape: "circle", id:1, location: 2}
]

@@

```{r rsaModel}
rsaModel <- 'var ObjectPrior = Categorical({vs: all_objects, ps: priorProbs })

var pragmaticListener = function(utterance){
Infer({method: "enumerate", model: function(){
var lexiconName = sample(LexiconPrior);
var obj = sample(ObjectPrior);
var S1 = speaker(obj, lexiconName);
observe(S1, utterance)
return {lexicon: lexiconName, obj: obj.shape}
}})
}

var speakerOptimality = 2.25;

var speaker = function(obj, lexiconName){
Infer({method: "enumerate", model: function(){
var utterance = utterancePrior(obj, lexiconName);
var L0 = literalListener(utterance);
 factor(speakerOptimality * L0.score(obj.shape))
return utterance
}})
}

var literalListener = function(utterance){
Infer({method: "enumerate", model: function(){
var lexiconName = sample(LexiconPrior); 
var lexicon = lexiconObject[lexiconName];
var obj = sample(ObjectPrior);
if ("label" in utterance) {
 var truthValue = lexicon(utterance, obj);
 condition(truthValue)
}
if (utterance.point) {
 var truthValuePoint = point(utterance, obj);
 condition(truthValuePoint)
}
return obj.shape 
}})
}

pragmaticListener({label: "dax", point: 2 })
'
```

```{r rsa model2, include = FALSE}
rsaModel2 <- '
var pragmaticListener = function(utterance, priorProbs){
Infer({method: "enumerate", model: function(){
var lexiconName = sample(LexiconPrior);
var obj = sample( Categorical({vs: all_objects, ps: priorProbs}));
var S1 = speaker(obj, lexiconName, priorProbs);
observe(S1, utterance)
return obj.shape == "circle" ? 1 : 0
}})
}

var speakerOptimality = 2.25;

@@

```{r model setup, include = FALSE}

strongPriorProbs <- data.frame(
  Experiment = c("Preference","Preference","Preference","Preference","Novelty","Novelty","Novelty","Novelty"),
  Change = c("Same speaker","Same speaker","Different speaker","Different speaker","Same speaker","Same speaker","Different speaker","Different speaker"),
  Alignment = c("Congruent","Incongruent","Congruent","Incongruent","Congruent","Incongruent","Congruent","Incongruent"),
  Prior = rep("Strong",8))

strongPriorProbs$priorProbs = list(
    c(0.0333333, 0.033333, 0.9666667), 
    c(0.9666667, 0.9666667, 0.0333333),
    c(0.3583333, 0.3583333, 0.6416667),
    c(0.6416667, 0.6416667, 0.3583333),
    c(0.1666667, 0.1666667, 0.8333333),
    c(0.8333333, 0.8333333, 0.1666667),
    c(0.4083333, 0.4083333, 0.5916667),
    c(0.5916667, 0.5916667, 0.4083333))

mediumPriorProbs <- data.frame(
  Experiment = c("Preference","Preference","Preference","Preference","Novelty","Novelty","Novelty","Novelty"),
  Change = c("Same speaker","Same speaker","Different speaker","Different speaker","Same speaker","Same speaker","Different speaker","Different speaker"),
  Alignment = c("Congruent","Incongruent","Congruent","Incongruent","Congruent","Incongruent","Congruent","Incongruent"),
  Prior = rep("Medium",8))

mediumPriorProbs$priorProbs = list(
    c(0.1465517, 0.1465517, 0.8534483), 
    c(0.8534483, 0.8534483, 0.1465517),
    c(0.4137931, 0.4137931, 0.5862069),
    c(0.5862069, 0.5862069, 0.4137931),
    c(0.2983871, 0.2983871, 0.7016129),
    c(0.7016129, 0.7016129, 0.2983871),
    c(0.4274194, 0.4274194, 0.5725806),
    c(0.5725806, 0.5725806, 0.4274194))

weakPriorProbs <- data.frame(
  Experiment = c("Novelty","Novelty","Novelty","Novelty"),
  Change = c("Same speaker","Same speaker","Different speaker","Different speaker"),
  Alignment = c("Congruent","Incongruent","Congruent","Incongruent"),
  Prior = rep("Weak",4))

weakPriorProbs$priorProbs = list(
  c(0.4166667, 0.4166667, 0.5833333), 
  c(0.5833333, 0.5833333, 0.4166667),
  c(0.475, 0.475, 0.5250000),
  c(0.5250000, 0.5250000, 0.475))

predPriorProbs = rbind(strongPriorProbs,mediumPriorProbs,weakPriorProbs)

allPriorProbs <- strongPriorProbs %>%
  select(-Prior)

allConditions <- predPriorProbs %>%
  filter(Prior == "Strong")%>%
  select(-priorProbs, -Prior)

newConditions <- predPriorProbs %>%
  select(-priorProbs)

predData <- data %>%
  mutate(Prior = "Strong")
```

```{r model rsa noise, include = FALSE}
predictions.rsa.noise <-'
var allConditions = dataFromR.newConditions
var allData = dataFromR.predData
var allPriorProbs = dataFromR.predPriorProbs

var model = function(){
   var noise = uniformDrift({a: 0, b:1, width: 0.1})

  var conditionOutput = map(function(conditionInfo){

  var conditionSpecificData =  _.filter(allData, {Experiment: conditionInfo.Experiment, Change: conditionInfo.Change, Alignment: conditionInfo.Alignment, Prior :"Strong"})

   var conditionSpecificPriors =  _.filter(allPriorProbs, {Experiment: conditionInfo.Experiment, Change: conditionInfo.Change, Alignment: conditionInfo.Alignment, Prior :"Strong"})

   var modelPredictions = pragmaticListener({label: "dax", point: 2 }, conditionSpecificPriors[0].priorProbs)
   var noisyModelPredictions = addNoise(modelPredictions, noise)

   map(function(d){ 
      observe(noisyModelPredictions, d.correct_inf)
    }, conditionSpecificData)

  return  [conditionInfo.Experiment + "_" + conditionInfo.Change + "_" +  conditionInfo.Alignment+ "_" + conditionInfo.Prior, Math.exp(noisyModelPredictions.score(1))]

}, allConditions)

 // return extend(_.fromPairs(conditionOutput), {noise: noise})

// generate predictions for new conditions

   var newPredictions = map(function(conditionInfo){

    var newSpecificPriors =  _.filter(allPriorProbs, {Experiment: conditionInfo.Experiment, Change: conditionInfo.Change, Alignment: conditionInfo.Alignment, Prior: conditionInfo.Prior})

    var newModelPredictions = pragmaticListener({label: "dax", point: 2 }, newSpecificPriors[0].priorProbs)
    var newNoisyModelPredictions = addNoise(newModelPredictions, noise)

    return  [conditionInfo.Experiment + "_" + conditionInfo.Change + "_" +  conditionInfo.Alignment + "_" + conditionInfo.Prior, Math.exp(newNoisyModelPredictions.score(1))]

  }, allConditions)

  return extend(_.fromPairs(newPredictions), {noise: noise})

@@

```{r predictions rsa noise, include = FALSE}
bda.pred.noise <- webppl(
  program_code = paste(rsaUtils, rsaModel2, predictions.rsa.noise, sep='\n'),
  data = list(allData = data, newConditions = newConditions, predPriorProbs = predPriorProbs, predData = predData), 
  data_var = "dataFromR",
  model_var = "model",
  inference_opts = list(method = "MCMC", samples = 10000, burn = 2000, verbose = T)
)

#bda.pred.noise2 has 100k samples

## distribution of noise
posterior.noise.pred <- bda.pred.noise %>%
  filter(Parameter %in% c("noise", "priorExponent"))

ggplot(posterior.noise.pred, aes(x = value))+
  geom_histogram()+
  facet_wrap(~Parameter, scales = 'free')

noisy.rsa.params.pred <- bda.pred.noise %>%
  filter(Parameter %in% c("noise", "priorExponent"))  %>%
  group_by(Parameter) %>%
  summarise(mean = estimate_mode(value), ci_lower = hdi_lower(value), ci_upper = hdi_upper(value))

noisy.rsa.params.pred100k <- bda.pred.noise2 %>%
  filter(Parameter %in% c("noise", "priorExponent"))  %>%
  group_by(Parameter) %>%
  summarise(mean = estimate_mode(value), ci_lower = hdi_lower(value), ci_upper = hdi_upper(value))

# model predictions

noisy.rsa.pred <- bda.pred.noise %>%
  filter(!(Parameter %in% c("noise", "priorExponent")))  %>%
  separate(Parameter, into = c("Experiment", "Change", "Alignment", "Prior"), sep="_")%>%
  mutate(Model="Noisy RSA Model",
         Adjustment = "Noise",
         Type = "RSA",
         Prior = relevel(as.factor(Prior), ref = "Weak"))%>%
  group_by(Model,Prior,Adjustment,Type,Experiment,Change,Alignment) %>%
  summarise(mean = estimate_mode(value), ci_lower = hdi_lower(value), ci_upper = hdi_upper(value))

```{r plot rsa noise pred}

ggplot(noisy.rsa.pred, 
       aes(x = Change, y = mean, fill = Alignment)) +
  geom_bar(stat="identity", position = position_dodge(), color = 'black') + 
  geom_hline(yintercept = 0.5, lty=2)+
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper),position = position_dodge(width = 0.9))+
  labs(x=" ",y="Proportion Choosing More Informative")+
  facet_grid(Experiment ~ Prior)+
  theme_few(base_size = 12) + 
  theme(axis.text.x=element_text(angle = 45, vjust = 1, hjust = 1))+
  ylim(0,1)
```

```{r model prior only noise , include = FALSE}
predictions.prior.noise <-'
var allConditions = dataFromR.newConditions
var allData = dataFromR.predData
var allPriorProbs = dataFromR.predPriorProbs

var model = function(){
   var noise = uniformDrift({a: 0, b:1, width: 0.1})

  var conditionOutput = map(function(conditionInfo){

  var conditionSpecificData =  _.filter(allData, {Experiment: conditionInfo.Experiment, Change: conditionInfo.Change, Alignment: conditionInfo.Alignment, Prior :"Strong"})

   var conditionSpecificPriors =  _.filter(allPriorProbs, {Experiment: conditionInfo.Experiment, Change: conditionInfo.Change, Alignment: conditionInfo.Alignment, Prior :"Strong"})

  var modelPredictions = Infer({method: "enumerate", model: function(){
      var obj = sample( Categorical({vs: all_objects, ps: conditionSpecificPriors[0].priorProbs}));
      return obj.shape == "circle" ? 1 : 0
  }})

   var noisyModelPredictions = addNoise(modelPredictions, noise)

   map(function(d){ 
     // display(JSON.stringify(noisyModelPredictions) + JSON.stringify(d.correct_inf))
      observe(noisyModelPredictions, d.correct_inf)
    }, conditionSpecificData)

  return  [conditionInfo.Experiment + "_" + conditionInfo.Change + "_" +  conditionInfo.Alignment, Math.exp(noisyModelPredictions.score(1))]

}, allConditions)

 // return extend(_.fromPairs(conditionOutput), {noise: noise})

// generate predictions for new conditions

   var newPredictions = map(function(conditionInfo){

    var newSpecificPriors =  _.filter(allPriorProbs, {Experiment: conditionInfo.Experiment, Change: conditionInfo.Change, Alignment: conditionInfo.Alignment, Prior: conditionInfo.Prior})

    var newModelPredictions = Infer({method: "enumerate", model: function(){
      var obj = sample( Categorical({vs: all_objects, ps: newSpecificPriors[0].priorProbs}));
      return obj.shape == "circle" ? 1 : 0
  }})

  var newNoisyModelPredictions = addNoise(newModelPredictions, noise)

    return  [conditionInfo.Experiment + "_" + conditionInfo.Change + "_" +  conditionInfo.Alignment + "_" + conditionInfo.Prior, Math.exp(newNoisyModelPredictions.score(1))]

  }, allConditions)

  return extend(_.fromPairs(newPredictions), {noise: noise})

```{r predictions prior only noise, include = FALSE}
bda.pred.prior.noise <- webppl(
  program_code = paste(rsaUtils, rsaModel2, predictions.prior.noise, sep='\n'),
  data = list(allData = data, newConditions = newConditions, predPriorProbs = predPriorProbs, predData = predData), 
  data_var = "dataFromR",
  model_var = "model",
  inference_opts = list(method = "MCMC", samples = 10000, burn = 2000, verbose = T)
)

## distribution of noise
posterior.prior.noise.pred <- bda.pred.prior.noise %>%
  filter(Parameter %in% c("noise", "priorExponent"))

ggplot(posterior.prior.noise.pred, aes(x = value))+
  geom_histogram()+
  facet_wrap(~Parameter, scales = 'free')

noisy.prior.params.pred <- bda.pred.prior.noise %>%
  filter(Parameter %in% c("noise", "priorExponent"))  %>%
  group_by(Parameter) %>%
  summarise(mean = estimate_mode(value), ci_lower = hdi_lower(value), ci_upper = hdi_upper(value))

# model predictions

prior.noise.pred <- bda.pred.prior.noise %>%
  filter(!(Parameter %in% c("noise", "priorExponent")))  %>%
  separate(Parameter, into = c("Experiment", "Change", "Alignment", "Prior"), sep="_")%>%
  mutate(Model="Noisy Prior only Model",
         Adjustment = "Noise",
         Type = "Prior only",
         Prior = relevel(as.factor(Prior), ref = "Weak"))%>%
  group_by(Adjustment,Model,Prior,Type,Experiment,Change,Alignment) %>%
  summarise(mean = estimate_mode(value), ci_lower = hdi_lower(value), ci_upper = hdi_upper(value))

```{r plot prior only noise regularized}

ggplot(prior.noise.pred, 
       aes(x = Change, y = mean, fill = Alignment)) +
  geom_bar(stat="identity", position = position_dodge(), color = 'black') + 
  geom_hline(yintercept = 0.5, lty=2)+
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper),position = position_dodge(width = 0.9))+
  labs(x=" ",y="Proportion Choosing More Informative")+
  facet_grid(Experiment ~ Prior)+
  theme_few(base_size = 12) + 
  theme(axis.text.x=element_text(angle = 45, vjust = 1, hjust = 1))+
  ylim(0,1)
```

```{r}
pred.plot <- bind_rows(prior.noise.pred,noisy.rsa.pred)

ggplot(pred.plot, 
       aes(x = Change, y = mean, fill = Alignment)) +
  geom_bar(stat="identity", position = position_dodge(), color = 'black') + 
  geom_hline(yintercept = 0.5, lty=2)+
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper),position = position_dodge(width = 0.9))+
  labs(x=" ",y="Proportion Choosing More Informative")+
  facet_grid(Experiment ~ Prior*Type)+
  theme_few(base_size = 12) + 
  theme(axis.text.x=element_text(angle = 45, vjust = 1, hjust = 1))+
  ylim(0,1)

```{r}
save.image(file="model.predictions.RData")
```

>>>>

---
title: "MCC Kids Model Predictions"
author: "Manuel Bohn"
output: html_document
---

```{r}
knitr::opts_chunk$set(echo = TRUE)
```

```{r setup, include=FALSE}
library(tidyverse)
library(knitr)
library(ggthemes)
library(langcog)
library(rwebppl)
library(coda)

@@

```
# Pretest

Loading data

```{r pretest data}

pref_data <- read_csv(file="data/kids_pref_data.csv")%>%
  filter(age != "2",
         trial_type != "train")%>%
  mutate(age_bin = factor(age),
         experiment = "preference_pretest",
         condition = ifelse(change == "false", "same_speaker", "different_speaker"),
         agent = ifelse( change == "false", agent, altAgent))%>%
  select(experiment,subid,age_bin,age_num,trial,condition,agent,correct)

inf_data <- read_csv(file="data/kids_inf_data.csv")%>%
  filter(subage != "2",
         trial != "filler1",
         trial != "filler2")%>%
  mutate(age_bin = factor(subage),
         experiment = "informativeness_pretest",
         condition = ifelse(control == "no", "test", "control"))%>%
  select(experiment,subid,age_bin,age_num,trial,condition,agent,correct)

pre_data <- bind_rows(pref_data,
                      inf_data)

@@

# Pretest results

```{r pretest plot}

pre_p1 <- pre_data %>%
  group_by(experiment,condition,age_num,subid)%>%
  summarise(correct = mean(correct))

ggplot(data = pre_p1, aes(x = age_num, y = correct, col = condition)) +
  geom_smooth(method = "lm", se = F)+
  geom_jitter(alpha = .5, height = 0, width = 0)+
  geom_hline(yintercept = 0.5, lty=2)+
  facet_wrap(~experiment)+
  labs(x="",y="Proportion Expected Choice")+
  theme_few() +
  ylim(-0.05,1.05)+
  guides(alpha = F)+ 
  scale_colour_solarized()

# Model predictions

## Pretest slopes
```{r rsaUtils, include = FALSE}
rsaUtils <- '
var all_objects = [
{ shape: "triangle", id:1, location: 1},  
{ shape: "triangle", id:2, location: 2},
{ shape: "circle", id:1, location: 2}
]

@@

```{r rsa model, include = FALSE}

rsaModel <- '

var pragmaticListener = function(utterance, priorProbs){
Infer({method: "enumerate", model: function(){
var lexiconName = sample(LexiconPrior);
var obj = sample( Categorical({vs: all_objects, ps: priorProbs}));
var S1 = speaker(obj, lexiconName, priorProbs);
observe(S1, utterance)
return obj.shape == "circle" ? 1 : 0
}})
}

@@

```{r speaker optimality slope}
soSlopeWebppl <- '

var infData = dataFromR.infData
var priorProbs = [.5, .5, .5]

var model  = function(){

  var so_slope = uniform(-5, 5)
  var so_int = uniform(0, 20)

    map(function(age){

      var speakerOptimality = so_int  + so_slope * (age - infData.minage)
      var rsaPredictions = pragmaticListener({label: "dax", point: 2 }, priorProbs)

      observe(rsaPredictions, infData.correct)

      return  [infData.experiment + "_" + infData.age_num, Math.exp(model.score(1))]

    }, infData.age_num)

@@

```{r}
soSlope <- webppl(
  program_code = paste(rsaUtils, rsaModel, soSlopeWebppl , sep='\n'),
  data = list(infData = inf_data%>%mutate(minage = min(age_num))), 
  data_var = "dataFromR",
  model_var = "model",
  inference_opts = list(method = "MCMC", samples = 2000, burn = 500, verbose = T)
)
```

```{r}
save.image(file="kids_ex3_predictions.RData")
```

### 2018-11-23 stats/kids_pref.Rmd
start working on kids model predictions

d_ipad <- read_csv(file="kids_pref.data.csv")

d_hand_code <- read.csv(file="kids_pref_handcoding.data.csv", sep = ";")%>%
  mutate(age_num = as.numeric(as.character(age_num)))

d <- bind_rows(d_ipad,d_hand_code)%>%
  mutate(trial_type = ifelse(trial == "train", "train", "test"))%>%
  filter(subid != "200718_8_pref")

# check if someone needs to be excluded because wrong in training
# no one
d %>%
  filter(trial_type == "train") %>%
  group_by(subid)%>%
  summarise(correct = mean(correct)) %>%
  filter(correct == 0)

>>>>

# d_ipad <- read_csv(file="kids_pref.data.csv")
# 
# d_hand_code <- read.csv(file="kids_pref_handcoding.data.csv", sep = ";")%>%
#   mutate(age_num = as.numeric(as.character(age_num)))
# 
# d <- bind_rows(d_ipad,d_hand_code)%>%
#   mutate(trial_type = ifelse(trial == "train", "train", "test"))%>%
#   filter(subid != "200718_8_pref")
# 
# 
# # check if someone needs to be excluded because wrong in training
# # no one
# d %>%
#   filter(trial_type == "train") %>%
#   group_by(subid)%>%
#   summarise(correct = mean(correct)) %>%
#   filter(correct == 0)

d <- read_csv(file="data/kids_pref_data.csv")
